Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2020-07-27 paper/notes.tex
A few notes, prior to actually creating configs for all these expts.

The orthogonal gradients in the current model which signal growth direction of
axonal growth cones naturally provide the vector signals which ensure that
regardless of entry point, growth cones tend towards their correct location.

@@

\subsubsection{Rotation experiments}

@@

@@

@@

@@

>>>>

The orthogonal gradients in the current model which signal growth direction of
axonal growth cones naturally provide the vector signals which ensure that
regardless of entry point, growth cones tend towards their correct
location. Can prove with different distributions of initial branching density
($a(\mb{x},t=0)$).

@@

To do: implement a HexGrid whose boundary increases with time. That will mean
some tampering with \code{morph::HexGrid}.

\subsubsection{Rotation experiments)}

@@

These correspond to \cite{goodhill_retinotectal_1999}, Figs.~2B--D and can
include retinal rotation as well as early/late tectal rotations.

The model as it stands contains an assumption about the orientation of the
guidance gradients. So rotating the tectum early enough means making no change
(given that I have no model for \emph{creating} the guidance gradients).

@@

I need to examine more carefully the timeline of these experiments.

These correspond to \cite{goodhill_retinotectal_1999}, Figs.~2E and 2F.

@@

These correspond to \cite{goodhill_retinotectal_1999}, Figs.~2I and 2J.

@@

This corresponds to \cite{goodhill_retinotectal_1999}, Fig 2H.
